MATH 3610 - Project \#1

### 2015-09-29 proj1.tex
modified

\begin{thebibliography}{9}
\bibitem{walph}
	Wolfram Research Inc.,
	\emph{WolframAlpha},
	Retrieved September 26, 2015
	http://www.wolframalpha.com/input/?i=%E2%88%AB+e^%28-a+x^2+%2B+b+x%29+dx
	http://www.wolframalpha.com/input/?i=ds%2Fdt+%3D+r+s+%28K+-+s+-+a+t%29
\end{thebibliography}

>>>>

\subsection{Disease Spread between Coupled Populations}

Consider three populations, with two connected only by an intermediate
	one.

\begin{align*}
\frac{d\widetilde{I}_1}{dt} & = \left( \left( r_{11} K_1 \right) \widetilde{I}_1 
			+ \left( r_{12} K_2 \right)  \widetilde{I}_2 \right)
		\left( 1 - \widetilde{I}_1 - \left( \frac{\alpha_1}{K_1} \right) t \right)\\
\frac{d\widetilde{I}_2}{dt} & = \left( \left( r_{22} K_2 \right) \widetilde{I}_2 
			+ \left( r_{21} K_1 \right)  \widetilde{I}_1 
			+ \left( r_{23} K_3 \right) \widetilde{I}_3 \right)
		\left( 1 - \widetilde{I}_2 - \left( \frac{\alpha_2}{K_2} \right) t \right)\\
\frac{d\widetilde{I}_3}{dt} & = \left( \left( r_{33} K_3 \right) \widetilde{I}_3 
			+ \left( r_{32} K_2 \right)  \widetilde{I}_2 \right)
		\left( 1 - \widetilde{I}_3 - \left( \frac{\alpha_3}{K_3} \right) t \right)
\end{align*}

If the second population is relatively small, then we might be able to 
	decrease the total number of infections by focusing our entire efforts
	on the smallest population to cut the link between the two populations.
We then treat the vaccination problem as a pareto optimization problem, to distribute
	the vaccines amongst the two populations.
However this may not be better than splitting the vaccinations between the two.

\begin{thebibliography}{9}
\bibitem{walph}
	Wolfram Research Inc.,
	\emph{WolframAlpha},
	Retrieved September 26, 2015
	http://www.wolframalpha.com/input/?i=\%E2\%88\%AB+e\^\%28-a+x\^2+\%2B+b+x\%29+dx
	http://www.wolframalpha.com/input/?i=ds\%2Fdt+\%3D+r+s+\%28K+-+s+-+a+t\%29
\end{thebibliography}
